Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex

\section{Experimental evaluation: \skug{Full: 3, Polished: 3}}
\label{sec:expe}

\subsection{Setup: \skug{Full: 5, Polished: 4}}
    \label{sec:setup}

@@

    \subsection{Results \skug{Full: 3, Polished: 2}}

@@

    \subsubsection{Dynamic experiments}
    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan withjout recomputation. $13$ experiments ended with a valid makespan after recomputation in case of \heft,
   $16$ in case of \heftmm, $50$ in case of \heftblc and $55$ in case of \heftbl.
    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    There were valid final makespans with no recomputation only for the smallest workflows - $56$ original ones, $47$ 200-task ones,
    $25$ 1000-task ones and $6$ 2000-task ones.

@@

    \subsubsection{Running times of the algorithm}
    To be able to answer the runtime system without holding it up for too long, the scheduler needs to provide a fast answer.
    Our bottom-level-based heuristics \heftbl and \heftblc provide smaller running times and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-abs} and Fig.~\ref{fig:runtimes-abs}).
    Their running times are similar and grow from tens of miliseconds for the smallest workflows to $25-27$ seconds for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks of the tasks,
    so its runnning time scales from also rens of miliseconds for the smalest workflows to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased running time is, though, offset by the unique $100\%$ success rate this algorithm shows when scheduling large
    workflows in difficult (memory-constrained) setups.

@@

    \subsubsection{Summary}

>>>>

\section{Experimental evaluation} %: \skug{Full: 3, Polished: 3}}
\label{sec:expe}

We first describe the experimental setup in Section~\ref{sec:setup}. 
Then, we report results on static experiments to assess the performance
of the memory-aware heuristics in Section~\ref{sec.expe.static}, before
discussing the heuristics behavior in a dynamic setting in Section~\ref{sec.expe.dyn}. 
Finally, we report running times of the heuristics in Section~\ref{sec.expe.t}.

\subsection{Experimental setup} %: \skug{Full: 5, Polished: 4}}
    \label{sec:setup}

@@

\subsection{Results in a static setting} % \skug{Full: 3, Polished: 2}}
\label{sec.expe.static}

@@

\subsection{Dynamic experiments}
\label{sec.expe.dyn}

    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan withjout recomputation. $13$ experiments ended with a valid makespan after recomputation in case of \heft,
   $16$ in case of \heftmm, $50$ in case of \heftblc and $55$ in case of \heftbl.
    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    There were valid final makespans with no recomputation only for the smallest workflows - $56$ original ones, $47$ 200-task ones,
    $25$ 1000-task ones and $6$ 2000-task ones.

@@

\subsection{Running times of the heuristics}
\label{sec.expe.t}

    To be able to answer the runtime system without holding it up for too long, the scheduler needs to provide a fast answer.
    Our bottom-level-based heuristics \heftbl and \heftblc provide smaller running times and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-abs} and Fig.~\ref{fig:runtimes-abs}).
    Their running times are similar and grow from tens of miliseconds for the smallest workflows to $25-27$ seconds for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks of the tasks,
    so its runnning time scales from also rens of miliseconds for the smalest workflows to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased running time is, though, offset by the unique $100\%$ success rate this algorithm shows when scheduling large
    workflows in difficult (memory-constrained) setups.

@@

%    \subsubsection{Summary}
